Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-28 paper/current/main.tex
edit math part

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned distances.
		Color indicates frequency of organization pairs within each hex bin.
		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding distance out-perform those made using geographic distance. 
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
		Embedding distance outperforms those made for geographic distance.
		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
	}
	\label{fig:gravity_performance}
\end{figure}

@@

And, if we remove ${\mu_*}$ for simplicity (or for our special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

where $v_w$ and $v'_w$ are `input' and `output' vector representations of each word in the vocabulary. With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq. \ref{eq:skipgram_conditional_expanded} and Eq. \ref{eq:real_embedding_relationship} share a similar functional form (or Eq.~\ref{eq:real_embedding_relationship} is a special case of Eq. ~\ref{eq:skipgram_conditional_expanded}).

>>>>

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding distance outperforms and is more robust than geographic distance.}
		\textbf{a.} embedding distance (cosine distance between organization vectors) explains more of the expected flux between organization pairs than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned distances.
		Color indicates frequency of organization pairs within each hex bin.
		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding distance out-perform those made using geographic distance. 
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
		Embedding distance outperforms those made for geographic distance.
		\textbf{g-h.} Embedding distance also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. \ref{fig:supp:gravity_prediction_subsets}).
		These predictions are robust whether the model is fit on the global data, or on the domestic (Fig.~\ref{fig:gravity_performance}e-h) or international Fig.~\ref{fig:supp:gravity_prediction_subsets}) subsets .
	}
	\label{fig:gravity_performance}
\end{figure}

@@

And, if we remove ${\mu_*}$ for simplicity (or for the special case with $\mu_{i} = \mu_{j} = \mu_*$), then $p(j|i)$ can be written as,

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
    \caption{Relationship between the conditional probability $p(j|i)$ from Eq.\ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary. With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq. \ref{eq:skipgram_conditional_expanded} and Eq. \ref{eq:real_embedding_relationship} share a similar functional form (or Eq.~\ref{eq:real_embedding_relationship} is a special case of Eq. ~\ref{eq:skipgram_conditional_expanded}).
